### 2020-09-02 Manuscript/pole_table_edited.tex
flip the polarity of Ediacaran poles within the figures and table, add more detail to Ediacaran pole discussion

            Laurentia &                             Carbon Butte/Awatubi &     NR &     248.5 &      35.2 & 163.8 &  14.2 &       3.5 &      751$^{+8}_{-8}$ &                                 \cite{Eyster2019a} \\                   Laurentia &                        Franklin event grand mean &      A &     275.4 &      73.0 & 162.1 &   6.7 &       3.0 &      724$^{+3}_{-3}$ &                               \cite{Denyszyn2009a} \\ \hline
                     Laurentia &                                 Long Range Dykes &      B &     303.3 &      53.7 & 355.3 &  19.0 &      17.4 &      615$^{+2}_{-2}$ &                                 \cite{Murthy1992a} \\ \hline
                     Laurentia &                         Baie des Moutons complex &      B &     301.0 &      50.8 & 321.5 & -34.2 &      15.4 &      583$^{+2}_{-2}$ &                             \cite{McCausland2011a} \\ \hline
                     Laurentia &                         Baie des Moutons complex &      B &     301.0 &      50.8 & 332.7 &  42.6 &      12.0 &      583$^{+2}_{-2}$ &                             \cite{McCausland2011a} \\ \hline
                     Laurentia &                       Callander Alkaline Complex &      B &     280.6 &      46.2 & 301.4 &  46.3 &       6.0 &      575$^{+5}_{-5}$ &                                 \cite{Symons1991a} \\ \hline
                     Laurentia &                                 Catoctin Basalts &      B &     281.8 &      38.5 & 296.7 &  42.0 &      17.5 &      572$^{+5}_{-5}$ &                                  \cite{Meert1994a} \\ \hline
                     Laurentia &                      Sept-Iles layered intrusion &      B &     293.5 &      50.2 & 321.0 & -20.0 &       6.7 &      565$^{+4}_{-4}$ &                                 \cite{Tanczyk1987a} \\ \hline

>>>>

            Laurentia &                             Carbon Butte/Awatubi &     NR &     248.5 &      35.2 & 163.8 &  14.2 &       3.5 &      751$^{+8}_{-8}$ &                                 \cite{Eyster2019a} \\ \hline
            Laurentia &                        Franklin event grand mean &      A &     275.4 &      73.0 & 162.1 &   6.7 &       3.0 &      724$^{+3}_{-3}$ &                               \cite{Denyszyn2009a} \\ \hline
                     Laurentia &                                 Long Range Dykes &      B &     303.3 &      53.7 & 175.3 & -19.0 &      17.4 &      615$^{+2}_{-2}$ &                                 \cite{Murthy1992a} \\ \hline
                     Laurentia &                         Baie des Moutons complex (A) &      B &     301.0 &      50.8 & 152.7 & -42.6 &      12.0 &      583$^{+2}_{-2}$ &                             \cite{McCausland2011a} \\ \hline
                     Laurentia &                         Baie des Moutons complex (B) &      B &     301.0 &      50.8 & 141.5 &  34.2 &      15.4 &      583$^{+2}_{-2}$ &                             \cite{McCausland2011a} \\ \hline
                     Laurentia &                       Callander Alkaline Complex &      B &     280.6 &      46.2 & 121.4 & -46.3 &       6.0 &      575$^{+5}_{-5}$ &                                 \cite{Symons1991a} \\ \hline
                     Laurentia &                                 Catoctin Basalts &      B &     281.8 &      38.5 & 116.7 & -42.0 &      17.5 &      572$^{+5}_{-5}$ &                                  \cite{Meert1994a} \\ \hline
                     Laurentia &                      Sept-Iles layered intrusion &      B &     293.5 &      50.2 & 141.0 &  20.0 &       6.7 &      565$^{+4}_{-4}$ &                                 \cite{Tanczyk1987a} \\ \hline
